Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
review DSVerifier Verification Flow

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

>>>>

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ represented by Eq.~\eqref{FWL_tf} 
(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ 
of the controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).
